---
title: "Homework2"
author: "Thomas Shi"
date: "2022/4/10"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)
abalone <- read_csv(file = "abalone.csv")
library(yardstick)
```

1

```{r, echo = T}
abalone <- read_csv(file = "abalone.csv")
abalone <- mutate(.data = abalone, age = 1.5 + rings )
abalone %>% head()
abalone %>% ggplot(aes(x = age)) +
  geom_histogram()
```
The distribution of age is roughly normal. However, it is a little bit right skewed with a long tail. Most abalones are between 7 and 15 years old



2

```{r, echo = T}
set.seed(3435)
abalone_split <- initial_split(abalone, prop = 0.75,
                                strata = age)
abalone_train <- training(abalone_split)
abalone_test <- testing(abalone_split)
abalone_train %>% head()
abalone_train %>% head()
```

3

```{r, echo = T}
abalone_train2 <- select(abalone_train, -rings)
abalone_recipe <- 
  recipe(age ~ ., data = abalone_train2) %>%
  step_dummy(type)

abalone_recipe <- abalone_recipe %>%
  step_interact(terms = ~ shucked_weight : starts_with('type'))

abalone_recipe <- abalone_recipe %>%
  step_interact(terms = ~ longest_shell : diameter)


abalone_recipe <- abalone_recipe %>%
  step_interact(terms = ~ shucked_weight : shell_weight)



abalone_recipe <- abalone_recipe %>% step_center(longest_shell, diameter, height, whole_weight,
                               shucked_weight, viscera_weight, shell_weight)

abalone_recipe <- abalone_recipe %>% step_scale(longest_shell, diameter, height, whole_weight,
                               shucked_weight, viscera_weight, shell_weight)

abalone_recipe



```
Since age = 1.5*rings, the relation between age and rings is fixed, so the model will be over optimized.
With rings, the model seems to be better than it should be, but it is not.

4

```{r, echo = T}
lm_model <- linear_reg() %>% 
  set_engine("lm")
```

5

```{r, echo = T}
lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(abalone_recipe)
```

6
```{r, echo = T}
lm_fit <- fit(lm_wflow, abalone_train2)
lm_fit %>% 
  extract_fit_parsnip() %>% 
  tidy()
type <- c('F')
longest_shell <- c(0.50)
diameter <- c(0.10)
height <- c(0.30)
whole_weight <- c(4)
shucked_weight <- c(1)
viscera_weight <- c(2)
shell_weight <- c(1)
an_abalone <- data.frame(type, longest_shell,diameter,height,whole_weight,
                         shucked_weight, viscera_weight, shell_weight)
an_abalone
predict(lm_fit, new_data = an_abalone)

```

7

```{r, echo = T}
abalone_metric <- metric_set(rsq, rmse, mae)
abalone_train_res <- predict(lm_fit, new_data = abalone_train2 %>% select(-age))
abalone_train_res <- bind_cols(abalone_train_res, abalone_train2 %>% select(age))
abalone_train_res %>% head()
abalone_metric(abalone_train_res, truth = age, 
                estimate = .pred)

```
R square is 0.5575
Root mean square error is 3.19879
Mean absolute error is 2.3066
R square being 0.5575 means that 55.75% of variability of Y can be explained by X
